Tuning for Software Analytics: is it Really Necessary?

### 2016-04-26 replytoreviewer.tex

\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\documentclass[final,twocolumn,5p]{elsarticle}
\begin{document}
\clearpage
\pagenumbering{roman}
\setcounter{page}{1} 
\section*{Reply to Reviews}

Thank your for your comments. The typos listed by reviewers
have been fixed and the remainder of the paper has been given
a careful proof read.

The reviewers raised certain issues which we respond  to as follows.-

{\it I am concerned about the reproduction of work from elsewhere. Although the relevant paper and book are cited in section 2.3 ([27, 28]) the amount of material that is reproduced is surprisingly large. I am also unsure what "presenting some new results from Rahman et al. [28]" actually means. It would obviously be wrong to present other researchers' results as if newly discovered but I doubt that this is the intention. Indeed, on checking the other paper, there is no obvious overlap. This needs to be clarified.}

Apologies to the reviewer for our unclear text that suggests
that this paper inappropriately copied  content from
elsewhere. This is not the case since nearly all of this paper has not been submitted
or published to another venue. The exception to that is:
\begin{itemize}
\item Section 2.3 and Table1 contains 1 page of tutorial material which we have adapted from other papers.
e.g. as the reviewer correctly points out,
the  'Easy to use' paragraph is taken nearly verbatim from [28], as are the 'widely-used', and 'useful' paragraphs.
\end{itemize}
Note that apart from Section 2.3,  10 of the 11 pages of this text are   completely new.

As to the reference to " presenting some new results from Rahman et al. [28]", that refers to one paragraph (120 words) end of section 2.3. 
Please note that we have removed the misleading text that raised that confusion
(start of 2.3).

{\em I think the way that the results are presented does not do justice to the findings in the abstract (that the improvements are large, and the tuning is simple). In particular, tables 8 and 9 are not very clear; why show the naive column?}

Thank for your that comment- we have simplified that presentation by separating the tuning \#evaluations from the runtimes-- see Table 8 and the new Table 9.

{\em I am distracted by the frequent use of footnotes. If the material is important and worthy of mention then it should be included in the main body of the paper. However, a reference to the relevant work may be sufficient and is sometimes preferable to using a footnote.}

Quite true- those footnotes are needlessly distracted.
They have now been incorporated into the text.

{\em  Eq 1 - what are d and T? - please use a where clause}

That where clause is now added after Equation 1. That clause says

\begin{quote} ... where  $d_i$ is the number of observed issues and $T$
is some threshold defined by an engineering judgement; we use $T=1$.\end{quote}

\end{document}

### 2016-04-26 old/dm101.tex
Updates from ShareLaTeX

Since programming inherently
introduces defects into  programs, it is important to test them before they're used.
Testing is expensive.
Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
For example, for  black-box testing methods,
a {\em linear} increase
in the confidence $C$ of finding  defects
can take {\em exponentially} more effort\footnote{A randomly selected 
input to a program will find a fault with probability $p$.
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=log(1 -
C)/log(1-p)$. For example, $N(0.90,10^{-3})=2301$
but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.}.
Exponential costs quickly exhaust finite resources so
standard practice is to apply the best
available  methods on code sections that seem   most critical. 
But 
any method that focuses on parts of the code
can blind us to defects in other areas. Some  {\em
lightweight sampling policy} should be used to explore the rest of the system.  This
sampling policy will always be incomplete.
Nevertheless, it is the only option when
resources prevent a complete assessment of everything.

>>>>

Since programming inherently
introduces defects into  programs, it is important to test them before they're used.
Testing is expensive.
Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
For example, for  black-box testing methods,
a {\em linear} increase
in the confidence $C$ of finding  defects
can take {\em exponentially} more effort:
\bi
\item
A randomly selected 
input to a program will find a fault with probability $p$.
\item
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. 
\item
Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=log(1 -
C)/log(1-p)$. 
\item
For example, $N(0.90,10^{-3})=2301$
but $N(0.98,10^{-3})=3901$; i.e. nearly double the number of tests.
\ei
Exponential costs quickly exhaust finite resources so
standard practice is to apply the best
available  methods on code sections that seem   most critical. 
But 
any method that focuses on parts of the code
can blind us to defects in other areas. Some  {\em
lightweight sampling policy} should be used to explore the rest of the system.  This
sampling policy will always be incomplete.
Nevertheless, it is the only option when
resources prevent a complete assessment of everything.
